Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-16 write-ups/PLDI/paper.tex
Space

\paragraph{Results}
For each GPU, \mytab\ref{tab:overhead} shows the geometric mean and
maximum slowdown across all applications and inputs, with averages and
maxima computed over 10 runs per benchmark. For the maximum slowdowns,
we indicate which application and input was responsible. The slowdown is
below 2 even in the worst case, and closer to 1 on average. We consider
these results as encouraging, especially since the performance of our
prototype could clearly be improved upon if cooperative scheduling was
implemented directly in the GPU driver.

@@

Co-scheduling non-cooperative kernels that compute their workload using a single workgroup leads to almost no overhead, but the period is far too high to meet the needs
of any of our three workloads. For example, a heavy workload averages a
period of 939 ms. As more workgroups are dedicated to non-cooperative
kernels, they execute quickly enough to be scheduled at the expected
period. More concretely, for the light and medium workloads, a quarter
of the workgroups executing the non-cooperative kernel are able to meet
their goal period (70 and 40 ms resp.). However, a quarter of the
workgroups are not sufficient to meet the goal for the heavy workload
(giving a mean period of 88 ms). Finally, if half of the workgroups are
allocated to the non-cooperative kernel, the heavy workload gets
averages \~10\% over its goal period (mean of 44 ms). If asking for all-but-one, the heavy workload can reach its goal period.
%
Yet, as expected, allocating more non-cooperative workgroups increases
the execution time overhead of the cooperative kernel.

>>>>

\paragraph{Results}
For each GPU, \mytab\ref{tab:overhead} shows the geometric mean and
maximum slowdown across all applications and inputs, with averages and
maxima computed over 10 runs per benchmark. For the maximum slowdowns,
we indicate which application and input was responsible. The slowdown is
below 2 even in the worst case, and closer to 1 on average. We consider
these results as encouraging, especially since the performance of our
prototype could clearly be improved upon in a native implementation.

@@

Co-scheduling non-cooperative kernels that compute their workload using a single workgroup leads to almost no overhead, but the period is far too high to meet the needs
of any of our three workloads. For example, a heavy workload averages a
period of 939 ms. As more workgroups are dedicated to non-cooperative
kernels, they execute quickly enough to be scheduled at the expected
period. More concretely, for the light and medium workloads, a quarter
of the workgroups executing the non-cooperative kernel are able to meet
their goal period (70 and 40 ms resp.). However, a quarter of the
workgroups are not sufficient to meet the goal for the heavy workload
(giving a mean period of 88 ms). Finally, if half of the workgroups are
allocated to the non-cooperative kernel, the heavy workload averages \~10\% over its goal period (mean of 44 ms). If asking for all-but-one, the heavy workload can reach its goal period.
%
Yet, as expected, allocating more non-cooperative workgroups increases
the execution time overhead of the cooperative kernel.
